In this section, we give the construction of the DV-NIZK scheme.
This can be seen as an instantiation of the DV-NIZK proposed in~\cite{DBLP:conf/pkc/ChaidosG15}
We will prove an encryption is an encryption of $0$ or $1$ under the PLWE encryption scheme.

\begin{description}
\item[$\Setup(1^\lambda)$]: where $\lambda$ is the security parameter.
  \begin{enumerate}
    \item Generate the parameters for the underlying encryption scheme.
      \begin{enumerate}
      \item Sample a polynomial $s_{RGSW} \sample \mathcal{D}_{\R_q, \sigma_{(k,RGSW)}}$
        \todo[inline]{Precisely define somewhere the deviation of the Gaussian distribution used here and same for the other deviation}
      \item Uniformly sample $a_{RGSW} \sample \R_q$ and a noise polynomial $e_{RGSW} \sample \mathcal{D}_{\R_q, \sigma_{(k, RGSW)}}$.
      \item Compute $b_{RGSW} = s_{RGSW} \cdot a_{RGSW} + e_{RGSW} \in \R_q$
      \item Set secret key and public key of the underlying Ring-GSW encryption scheme:
        \begin{align*}
          \vec{s}_{RGSW} &= \begin{bmatrix} 1 \\ -s_{RGSW} \end{bmatrix}  & \vec{a}_{RGSW} &=  \begin{bmatrix} b_{RGSW} \\ a_{RGSW}\end{bmatrix}
        \end{align*}
      \item Sample a polynomial $s_0 \sample \mathcal{D}_{(\R_q, \sigma_{BV})}$, $a_0 \sample \R_q$ and $e_0 \sample \mathcal{D}_{(\R_q, \sigma_{BV})}$.
      \item Set $b_0 = a_0 s_0 + 2 e_0$.
      \item Set secret key and public key of the underlying Ring-LWE encryption scheme:
        \begin{align*}
          \vec{s} &= \begin{bmatrix} 1 \\ -s_0\end{bmatrix} & \vec{a} &= \begin{bmatrix} a_0 \\ b_0\end{bmatrix}
        \end{align*}
      \end{enumerate}
    \item Sample a uniformly random polynomial $d \sample \R_2$.
    \item Encrypt the message with the two underlying encryption schemes:
      \begin{enumerate}
      \item Sample a $(N \times 1)-$matrix $\mat{R}_{RGSW} \sample (\R_q \cap\{0,1\})^{N \times 1}$.
      \item Sample a $(N \times 2)-$noise matrix $\mat{E}_{RGSW} \sample \mathcal{D}_{(\R_q^{N \times 2}, \sigma_{(c, RGSW)})}$.
      \item Sample polynomials $v,e' \sample \mathcal{D}_{(R_q, \sigma_{BV})}$ and $e'' \sample  \mathcal{D}_{(R_q, \sigma_{BV}')}$.
      \item Compute two polynomials $(a, b) \in \R_q^2$
      \item Compute the following ciphertexts
        \begin{align*}
          \mat{C}_d^{RGSW} &= \vec{a}_{RGSW} \cdot \mat{R}_{RGSW} + \mat{E}_{RSGW} +  d \cdot \mat{G} &
          \vec{c}_d &= \begin{bmatrix} b + \mu \\ -a \end{bmatrix}
        \end{align*}
      \end{enumerate}
    \item Set the public parameter and the secret verification key as follows:
      \begin{align*}
        \PPP &= (\vec{a}_{RGSW}, \vec{a}, \vec{c}_d, \mat{C}_d^{GSW}) & \SK &= (\vec{s}_{RGSW}, \vec{s})
      \end{align*}
  \end{enumerate}



\item[$\Prove(\PPP, \vec{c}, \mu, \vec{r}, \PK^P)$]: This algorithm produces a DV-NIZK proof of the following instance:
  \begin{align*}
    \vec{c} &= PLWE.\Enc(\PK^P, \mu; \vec{r}) \wedge \mu \in \{0,1\}
  \end{align*}
  \begin{enumerate}
  \item Parse $\PK^P, \vec{r}, \vec{c}$ as follows:
    \begin{align*}
      \PK^P &= \begin{bmatrix} b_0^P \\ a_0^P \end{bmatrix} &
      \vec{r} &= (v_c, e_c', e_c'')&
      \vec{c} &= \begin{bmatrix} c_0\\ c_1\end{bmatrix} = \begin{bmatrix} b_0^P v_c + 2 e_c'' + \mu \\ -a_0^Pv_c + 2 e_c'\end{bmatrix}
    \end{align*}
%  \item Parse the public parameter $\PPP$:
%    \begin{align*}
%      \PPP &= (\mat{A}_{RGSW}, \vec{a} = \begin{bmatrix} a_0 \\ b_0\end{bmatrix}, \vec{c}_d, \mat{C}_d^{GSW})
%    \end{align*}
  \item Uniformaly choose a non-zero ring element $\mu_a \sample \R_2 \backslash \{0\}$.
  \item Set $\mu_b = - \mu \cdot \mu_a$.
  \item Simple $v_a, e_a' \sample \mathcal{D}_{(\R_q, \sigma_{BV})}$, $e_a'' \sample \mathcal{D}_{(\R_q. \sigma_{BV}')}$ and $v_b, e_b' \sample \mathcal{D}_{(\R_q, \sigma_{BV})}$, $e_b'' \sample \mathcal{D}_{(\R_q. \sigma_{BV}')}$.
  \item Compute the ciphertexts
    \begin{align*}
      \vec{c}_a &= \begin{bmatrix} b_0^Pv_a + 2 e_a'' + \mu_a \\ - a_0^Pv_a + 2 e_a'\end{bmatrix} &
        \vec{c}_b &= \begin{bmatrix} b_0^Pv_b + 2 e_b'' + \mu_b \\ - a_0^Pv_b + 2 e_b'\end{bmatrix} 
    \end{align*}
  \item Compute the ciphertext $\vec{c}_f$
    \begin{align*}
      \vec{c}_f &= \mu \cdot \vec{c}_d + \mu_a \in \R_q^2
    \end{align*}
  \item We also compute the following ciphertext of the underlying Ring-GSW scheme:
    \begin{align*}
      \mat{C}_{r_f^0} &= \mat{C}_d^{RGSW} \cdot \mat{G}^{-1}(v \cdot \mat{G}) + v_a \cdot \mat{G} \\
      \mat{C}_{r_f^1} &= \mat{C}_d^{RGSW} \cdot \mat{G}^{-1}(e' \cdot \mat{G}) + e_a' \cdot \mat{G} \\
      \mat{C}_{r_f^2} &= \mat{C}_d^{RGSW} \cdot \mat{G}^{-1}(e'' \cdot \mat{G}) + e_a'' \cdot \mat{G} \\
      \mat{C}_{r_0^0} &= (\mat{C}_d^{RGSW} \cdot \mat{G}^{-1}(\mu \cdot \mat{G}) + \mu_a \cdot \mat{G} - \mat{C}_d^{RGSW}) \cdot \mat{G}^{-1}(v \cdot \mat{G}) + v_b \cdot \mat{G} \\
      \mat{C}_{r_0^1} &= (\mat{C}_d^{RGSW} \cdot \mat{G}^{-1}(\mu \cdot \mat{G}) + \mu_a \cdot \mat{G} - \mat{C}_d^{RGSW}) \cdot \mat{G}^{-1}(e' \cdot \mat{G}) + e_b' \cdot \mat{G} \\
      \mat{C}_{r_0^2} &= (\mat{C}_d^{RGSW} \cdot \mat{G}^{-1}(\mu \cdot \mat{G}) + \mu_a \cdot \mat{G} - \mat{C}_d^{RGSW}) \cdot \mat{G}^{-1}(e'' \cdot \mat{G}) + e_b'' \cdot \mat{G} \\
    \end{align*}
  \item Output the prove:
    \begin{align*}
      \pi &= (\vec{c}_a, \vec{c}_b, \vec{c}_f, \mat{C}_{r_f^0}, \mat{C}_{r_f^1}, \mat{C}_{r_f^2}, \mat{C}_{r_0^0}, \mat{C}_{r_0^1}, \mat{C}_{r_0^2}) 
    \end{align*}
  \end{enumerate}

\item[$\Verif(\PPP, \SK, \pi)$]: The verifier uses the secret key to verify the encryption is an encryption of a bit.
  \begin{enumerate}
  \item Parse the public parameter $\PPP = (\mat{A}_{RGSW}, \vec{a}, \vec{c}_d, \mat{C}_d^{GSW})$
  \item Parse the secret key $\SK = (\vec{s}_{RGSW}, \vec{s})$.
  \item Parse the prove $\pi = (\vec{c}_a, \vec{c}_b, \vec{c}_f, \mat{C}_{r_f^0}, \mat{C}_{r_f^1}, \mat{C}_{r_f^2}, \mat{C}_{r_0^0}, \mat{C}_{r_0^1}, \mat{C}_{r_0^2})$.
  \item Decrypt $\vec{c}_d$ and $\mat{C}_d^{RGSW}$.
    If $PLWE.\Dec(\vec{s}, \vec{c}_d) \neq RGSW.\Dec(\vec{s}_{RGSW}, \mat{C}_d^{RGSW})$ then return $\False$, else set $d = PLWE.\Dec(\vec{s}, \vec{c}_d)$.
  \item Decrypt the ciphertext and set:
    \begin{align*}
      f &= PLWE.\Dec(\vec{s}, \vec{c}_f)
    \end{align*}
  \item Decrypt the ciphertexts of the randomness and verify that they are all small:
    \begin{align*}
      v_f & = RGSW.\Dec(\vec{s}_{GSW}, \mat{C}_{r_f^0}) \leq B \\
      e_f' & = RGSW.\Dec(\vec{s}_{GSW}, \mat{C}_{r_f^1}) \leq B \\
      e_f'' & = RGSW.\Dec(\vec{s}_{GSW}, \mat{C}_{r_f^2}) \leq B' \\
      v_0 & = RGSW.\Dec(\vec{s}_{GSW}, \mat{C}_{r_0^0}) \leq B \\
      e_0' & = RGSW.\Dec(\vec{s}_{GSW}, \mat{C}_{r_0^1}) \leq B \\
      e_0'' & = RGSW.\Dec(\vec{s}_{GSW}, \mat{C}_{r_0^2}) \leq B' \\
    \end{align*}
    \todo[inline]{The security analysis need to be done for the exact value of B}
  \item Verify the following equations:
    \begin{align*}
      d \cdot \vec{c} + \vec{c}_a &= PLWE.\Enc(\PK^P = \vec{a}^P, f; (v_f, e_f', e_f''))\\
      (f-d) \cdot \vec{c} + \vec{c}_b &= PLWE.\Enc(\PK^P= \vec{a}^P, 0; (v_f, e_f', e_f''))
    \end{align*}
  \item If the proof $\pi$ verifies all the equations then the algorithm returns $\True$, otherwise it returns $\False$.
  \end{enumerate}
  
  
  
\end{description}
